---
title: "p8105_hw1_jl6049"
author: "LYU JING"
date: "9/23/2021"
output: github_document
---


## Problem 1

1. I am trying to create a dataframe as request.

```{r include = FALSE}
library(tidyverse)
```

```{r}
create_df = tibble(
  norm_samp = rnorm(10),
  logical_vec = norm_samp > 0,
  char_vec = c("a","b","c","d","e","f","g","h","i","j"),
  factor_vec = factor(c("small", "median","large","samll","median","large","samll","median","large", "samll"))
)
```

I have created a dataframe with a random sample, a logical vector, a character vector and a factor vector.


2. I am trying to take the mean of each variable in your dataframe.

- for the mean of random norm sample.
```{r}
mean_norm = mean(pull(create_df, norm_samp))
```

It works! It is `r mean_norm`

- for the mean of logical vector.
```{r}
mean_log = mean(pull(create_df, logical_vec))
```

It works! It is `r mean_log`

- for the mean of character vector.
```{r}
mean_char = mean(pull(create_df, char_vec))
```

It does not work.

- for the mean of factor vector.
```{r}
mean_factor = mean(pull(create_df, factor_vec))
```

It does not work.


3. I am trying to use as.numeric function on the logical, character, and factor variables to convert them to numeric.
```{r eval = FALSE}
numeric_logical = as.numeric(pull(create_df, logical_vec))
numeric_char = as.numeric(pull(create_df, char_vec))
numeric_factor = as.numeric(pull(create_df, factor_vec))
```

Result: as.numeric function could change the logical and factor variables into numbers, but it does not work on character vector.
That could because logical could be saved as "0" and "1" and factor could be saved as ordinal numbers. But character cannot be saved by numbers.

However, when it comes to get the mean, things could be different for factor variables. Because that the ordinal numbers cannot represent the actual meaning of the factor levels, so that we cannot get the mean of a factor by just calculate the relative number of the levels.



## Problem 2

1. Input data "penguins".
```{r}
data("penguins", package = "palmerpenguins")
```

2. get more knowledge about the dataset.
```{r eval = FALSE}
names(penguins)
nrow(penguins)
ncol(penguins)
mean_flipper = mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```

- The dataset contains 8 variables including `r names(penguins)`
- The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns
- The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`

3. Make a scatterplot!
```{r warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + labs(x = "Bill Length (mm)" , y = "Flipper Length (mm)")
```

4. Export my scatterplot
```{r warning = FALSE}
ggsave("scatterplot.png", height = 4, width = 6)
```




